### 2021-01-19 publications/2020-03-paper/abstract.tex
incorporates the last of kdh comments, closes #98 #99
Former-commit-id: a009126bcf29f293c8ef7aeda35d1402a6cfb4c2
Former-commit-id: bf3d6a2e2d208737784bc145af251c1a2db4774b

We simulated possible pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply sector using a single-region \gls{TIMES} model. Critically, our simulations incorporate novel technologies like hydrogen electrolysers, carbon capture, photochemical water splitting, and emerging photovoltaic cells, assess long-term impact up to the year 2100, and include life-cycle emissions and learning curves for parameters such as investment cost, efficiency, and emission coefficients. Results indicate that a hybrid approach, using nuclear power and hydrogen from renewable energy-based electrolysis, is cost-effective and provides long-term emission reduction along with energy security. Nuclear, wind, solar, and hydrogen from renewables emerge as key emission reduction technologies, while natural gas with carbon capture plays a minor role.

>>>>

We simulated possible pathways to meeting 2030 and 2050 emission targets within the Japanese electricity supply sector using a single-region model in \gls{TIMES}. Critically, our simulations incorporate novel technologies like hydrogen electrolysers, carbon capture, photochemical water splitting, and emerging photovoltaic cells, assess long-term impact up to the year 2100, and include life-cycle emissions and learning curves for parameters such as investment cost, efficiency, and emission coefficients. Results indicate that a hybrid approach, using nuclear power and hydrogen from renewable energy-based electrolysis, is cost-effective and provides long-term emission reduction along with energy security. Nuclear, wind, solar, and hydrogen from renewables emerge as key emission reduction technologies, while natural gas with carbon capture plays a minor role.

### 2021-01-19 publications/2020-03-paper/acks.tex
incorporates the last of kdh comments, closes #98 #99
Former-commit-id: a009126bcf29f293c8ef7aeda35d1402a6cfb4c2
Former-commit-id: bf3d6a2e2d208737784bc145af251c1a2db4774b

We are also grateful to Kenshi Itaoka and Hadi Farabi-Asl for providing valuable discussions related to this project, and to Gavin Davis and Nataly Panczyk for editing drafts.

>>>>

We are also grateful to Kenshi Itaoka and Hadi Farabi-Asl for providing valuable discussions related to this project, and to Gavin Davis and Nataly Panczyk for editing manuscript drafts.

### 2021-01-19 publications/2020-03-paper/introduction.tex
incorporates the last of kdh comments, closes #98 #99
Former-commit-id: a009126bcf29f293c8ef7aeda35d1402a6cfb4c2
Former-commit-id: bf3d6a2e2d208737784bc145af251c1a2db4774b

\section{Introduction} \label{Introduction}
In order to mitigate climate change and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalised this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. The largest contribution to global \gls{GHG} emissions, some 73\%, comes largely from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}. Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants. However, these options are not always economically feasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}. Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment \cite{international_energy_agency_latest_2019}.

Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan, recently updated to the 5th edition in 2018 \cite{meti_japans_2018}. The Basic Energy Plan outlines national policy toward a new energy system for the years 2030 and 2050, cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}. The plan reaffirms Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and the environment (summarised as `3E+S'; ibid). Although the Japanese 3E+S goals and the Paris Agreement targets have some parallels, the plan does not detail how the 2050 emission reduction target of 80\% is to be met. Matsuo et. al have suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by low-carbon technologies \cite{matsuo_quantitative_2018}. For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}. The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, meti_basic_2017}.

This research aims to investigate the likely suite of electricity generation and storage technologies, as well as their feasibility in meeting Japan's carbon reduction goals, while being cognizant of energy policy, resource limitations, demand growth, emerging technologies, and economic constraints using \gls{TIMES} framework. Our dynamic simulations of transition scenarios, which focus on minimising the cost of the transition while satisfying CO$_2$ emission constraints, suggest potential economically feasible decarbonisation pathways that meet the increasing near-term electricity demand. Additionally, we assess the significance of key economic parameters of emerging technologies through sensitivity analysis, in order to highlight the most impactful parameters and hence guide research and development efforts focused on these technologies.

>>>>

\section{Introduction} \label{Introduction}
In order to mitigate climate change and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalised this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. The largest contribution to global \gls{GHG} emissions, some 73\%, comes largely from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}. Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants. However, these options are often economically infeasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}. Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment \cite{international_energy_agency_latest_2019}.

Although influenced by the Paris Agreements, Japanese energy policy is governed by the Basic Energy Plan \cite{meti_japans_2018}, which outlines national policy towards a new energy system for the years 2030 and 2050 cognizant of limited indigenous resources, the impact of the Fukushima incident, and external pressures on energy supplies \cite{meti_annual_2018}. The plan reaffirms Japanese benchmarks for evaluating the energy system, first and foremost, within the context of energy security, followed by economic efficiency, safety, and the environment (summarised as `3E+S'; ibid). Although the Japanese 3E+S goals and the Paris Agreement targets have some parallels, the plan does not detail how the 2050 emission reduction target of 80\% is to be met. Matsuo et. al have suggested that electrification of a number of sectors will be required to achieve the ambitious 2050 target, underpinned by low-carbon technologies \cite{matsuo_quantitative_2018}. For the power sector to achieve such a target, near-zero emissions are required, and early action utilising existing technologies is preferable to delayed action utilising future technologies \cite{ashina_roadmap_2012}. The strategies currently under consideration include reinvigorating nuclear power, deploying \gls{CCS} to fossil fuel power plants, and ushering in a hydrogen economy based on renewable energy-based electrolysis as well as hydrogen imports from abroad \cite{ashina_roadmap_2012, matsuo_quantitative_2018, meti_basic_2017}.

This research aims to investigate the likely suite of electricity generation and storage technologies, as well as their feasibility in meeting Japan's carbon reduction goals, while being cognizant of energy policy, resource limitations, demand growth, emerging technologies, and economic constraints using the \gls{TIMES} framework. Our dynamic simulations of transition scenarios, which focus on minimising the cost of the transition while satisfying CO$_2$ emission constraints, suggest potential economically feasible decarbonisation pathways that meet the increasing near-term electricity demand. Additionally, we assess the significance of key economic parameters of emerging technologies through sensitivity analysis, in order to highlight the most impactful parameters and hence guide research and development efforts focused on these technologies.

### 2021-01-19 publications/2020-03-paper/litreview.tex
incorporates the last of kdh comments, closes #98 #99
Former-commit-id: a009126bcf29f293c8ef7aeda35d1402a6cfb4c2
Former-commit-id: bf3d6a2e2d208737784bc145af251c1a2db4774b

\section{Background and literature review} \label{litreview}
The Paris Agreement commits individual nations to significant carbon reduction over time through the \gls{INDC} mechanism \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: reduce GHG emissions by 26\% compared to 2013 levels by 2030, and reduce overall GHG emissions by 80\% or more by 2050, through the ``development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. 
Aware of these targets, many researchers have evaluated Japan's future energy system using a variety of modelling approaches, which we review below. Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al., found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 \cite{ozawa_hydrogen_2018}. Recognising the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency of renewables, Li et al. explored the role of hydrogen as a storage medium through power-to-gas approaches in Kyushu, Japan. Their study identified that power-to-gas can increase the effective utilisation rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues \cite{li_potential_2019}. Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach \cite{chapman_strategic_2018}. Considering Japan's economic conditions and demographic trends, such as moderate GDP growth and rapid ageing, Kuriyama et al. suggest that 2030 targets can be met or exceeded (with up to 42\% GHG reduction) with limited renewable energy growth and a 15\% contribution from nuclear, or without nuclear, under a renewable growth scenario \cite{kuriyama_can_2019}. However, these trends and energy system changes will likely be insufficient to meet the more ambitious 2050 targets.

Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, which would affect both CCS and nuclear deployment rates into the future. Consensus on policy options and priorities also has a large influence on modelling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 \cite{moinuddin_japan_2019}. A seminal work by Sugiyama et al. harmonises a number of modelling approaches for Japan's long-term (up to 2050) climate change mitigation options, utilising national and global general and partial equilibrium models \cite{sugiyama_japans_2019}. Model results are contrasted under six scenarios which incorporate a baseline, a range of emissions reductions (50-80\%), and regional obligations for global models (ibid.) under the Paris Agreement target of an 80\% reduction. Each of the models assessed recognise the importance of renewable energy deployment by 2050, notably hydro, solar, and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas. Additionally, for Japan, the option of importing carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, oshiro_diffusion_2015, sugiyama_japans_2019}. Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}. Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight fuel cell vehicles and power generation, via both mixed and direct combustion. Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal-fired power generation reduce toward 2050 \cite{ishimoto_significance_2017}. From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels, which requires a three-fold reduction in cost by 2030 and further reductions into the future \cite{nagashima_japans_2018}. Under the Basic Hydrogen Strategy, the Japanese government aims to realise low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalise regional areas, and develop hydrogen related technologies \cite{meti_basic_2017}. The strategy aims to account for both economic and geopolitical impacts and the need to prioritise research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}. A common thread across previous research is the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred after the Fukushima nuclear accident \cite{oshiro_mid-century_2019}.

>>>>

\section{Background and literature review} \label{litreview}
The Paris Agreement commits individual nations to significant carbon reduction over time through the \gls{INDC} mechanism \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. Japan, as a signatory to the Paris Agreements, has submitted an INDC with the following goals and timelines: reduce GHG emissions by 26\% compared to 2013 levels by 2030, and reduce overall GHG emissions by 80\% or more by 2050, through the ``development and diffusion of low-carbon technologies and transition to a low-carbon socio-economic structure" \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. 
Aware of these targets, many researchers have evaluated Japan's future energy system using a variety of modelling approaches, which we review below. Using the \gls{MARKAL} model, considering the uncertainties of technology development, Ozawa et al. found that hydrogen will play a major role in the future energy system, reliant on both nuclear power and \gls{CCS} to reduce electricity sector emissions to nearly zero by 2050 \cite{ozawa_hydrogen_2018}. Recognising the benefits that renewable energy will play in reducing carbon emissions, and the issues of intermittency of renewables, Li et al. explored the role of hydrogen as a storage medium through power-to-gas approaches in Kyushu, Japan. Their study identified that power-to-gas can increase the effective utilisation rate of renewable energy, and the use of hydrogen in the gas network, effectively pairing the electricity and gas networks, overcomes current renewable electricity curtailment issues \cite{li_potential_2019}. Cognizant of the Japanese government's strategic approach to carbon reduction out to 2050 via energy system reform, Chapman and Pambudi also identify a strong role for nuclear, renewables, and hydrogen under a carbon constrained, optimal cost MARKAL/TIMES simulation approach \cite{chapman_strategic_2018}. Considering Japan's economic conditions and demographic trends, such as moderate GDP growth and rapid ageing, Kuriyama et al. suggest that 2030 targets can be met or exceeded (with up to 42\% GHG reduction) with limited renewable energy growth and a 15\% contribution from nuclear, or without nuclear, under a renewable growth scenario \cite{kuriyama_can_2019}. However, these trends and energy system changes will likely be insufficient to meet the more ambitious 2050 targets.

Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, which would affect both CCS and nuclear deployment rates into the future. Consensus on policy options and priorities also has a large influence on modelling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 \cite{moinuddin_japan_2019}. A seminal work by Sugiyama et al. harmonises a number of modelling approaches for Japan's long-term (up to 2050) climate change mitigation options, utilising national and global general and partial equilibrium models \cite{sugiyama_japans_2019}. Model results are contrasted under six scenarios which incorporate a baseline, a range of emissions reductions (50-80\%), and regional obligations for global models (ibid.) under the Paris Agreement target of an 80\% reduction. Each of the models assessed recognise the importance of renewable energy deployment by 2050, notably hydro, solar, and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas. Additionally, for Japan, the option of importing carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, sugiyama_japans_2019}. Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}. Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight fuel cell vehicles and power generation, via both mixed and direct combustion. Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal-fired power generation reduce towards 2050 \cite{ishimoto_significance_2017}. From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels, which requires a three-fold reduction in cost by 2030 and further reductions into the future \cite{nagashima_japans_2018}. Under the Basic Hydrogen Strategy, the Japanese government aims to realise low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalise regional areas, and develop hydrogen related technologies \cite{meti_basic_2017}. The strategy aims to account for both economic and geopolitical impacts and the need to prioritise research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}. A common thread across previous research is the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred after the Fukushima nuclear accident \cite{oshiro_mid-century_2019}.

### 2021-01-19 publications/2020-03-paper/methods.tex
incorporates the last of kdh comments, closes #98 #99
Former-commit-id: a009126bcf29f293c8ef7aeda35d1402a6cfb4c2
Former-commit-id: bf3d6a2e2d208737784bc145af251c1a2db4774b

\section{Methodology} \label{method}
% what is TIMES
\subsection{TIMES Model Description}
\gls{TIMES} models dynamic energy systems and simulates transition scenarios as a mixed-integer linear optimisation problem that is subject to a primary objective function and additional constraints \cite{loulou_etsap-tiam_2008}. The generation, refinement, supply, storage, and trade of energy commodities across multiple sectors and multiple regions are modeled using a wide variety of in-built commodity and process types. Emissions can be associated with energy commodities or processes as an emission coefficient per unit commodity produced or consumed.

@@

\begin{table}[!ht]
	\caption{Candidate parameters and their variation in our sensitivity analysis.}
	\vspace{0.1in}
	\begin{tabularx}{0.9\textwidth}{p{0.3\textwidth} p{0.15\textwidth} p{0.15\textwidth}p{0.3\textwidth}}
\hline 
\textbf{Technology}  & \textbf{Sampled} & \textbf{Distribution}& \textbf{Distribution}\\
\textbf{Parameter} & \textbf{Distribution} & \textbf{Mean}& \textbf{Range}\\
\hline
\gls{PWS} Investment Cost       & Gaussian    & 3088 \$/kW & $\pm$20\% of mean. \\                  
\gls{SOEC} Investment Cost      & Gaussian    & 1388 \$/kW & $\pm$20\% of mean.\\                  
\gls{PEMEC} Investment Cost     & Gaussian    & 3800 \$/kW & $\pm$20\% of mean.\\                  
\gls{SOFC} Investment Cost      & Gaussian    & 7399 \$/kW & $\pm$20\% of mean.\\                  
\gls{PEMFC} Investment Cost     & Gaussian    & 7399 \$/kW & $\pm$20\% of mean.\\                  
\gls{CCS} Gas Investment Cost   & Gaussian    & 2626 \$/kW & $\pm$20\% of mean.\\                  
\gls{CCS} Coal Investment Cost  & Gaussian    & 5252 \$/kW & $\pm$20\% of mean.\\
\gls{PWS} Emission Coefficient  & Triangular  & 1.08 g/kWh & 0.2-5.405 g/kWh. \\                  
\gls{SOEC} Emission Coefficient & Triangular  & 1.08 g/kWh & 0.2-5.405 g/kWh. \\
\gls{PWS} Efficiency            & Triangular  & 0.525 & 0.5-0.58. \\                               
\hline
	\end{tabularx}
\label{sa-vars}
\end{table}

>>>>

\section{Methodology} \label{method}
% what is TIMES
\subsection{TIMES Model Description}
\gls{TIMES} models dynamic energy systems and simulates transition scenarios as a mixed-integer linear optimisation problem that is subject to a primary objective function and additional constraints \cite{loulou_etsap-tiam_2008}. The generation, refinement, supply, storage, and trade of energy commodities are modelled across multiple sectors and multiple regions using a wide variety of in-built commodity and process types. Emissions can be associated with energy commodities or processes as an emission coefficient per unit commodity produced or consumed.

@@

\begin{table}[!ht]
	\caption{Candidate parameters and their variation in our sensitivity analysis.}
	\vspace{0.1in}
	\begin{tabularx}{0.9\textwidth}{p{0.3\textwidth} p{0.15\textwidth} p{0.15\textwidth}p{0.3\textwidth}}
\hline 
\textbf{Technology}  & \textbf{Sampled} & \textbf{Distribution}& \textbf{Distribution}\\
\textbf{Parameter} & \textbf{Distribution} & \textbf{Mean}& \textbf{Range}\\
\hline
\gls{PWS} Investment Cost       & Gaussian    & 3088 \$/kW & $\pm$20\%. \\                  
\gls{SOEC} Investment Cost      & Gaussian    & 1388 \$/kW & $\pm$20\%.\\                  
\gls{PEMEC} Investment Cost     & Gaussian    & 3800 \$/kW & $\pm$20\%.\\                  
\gls{SOFC} Investment Cost      & Gaussian    & 7399 \$/kW & $\pm$20\%.\\                  
\gls{PEMFC} Investment Cost     & Gaussian    & 7399 \$/kW & $\pm$20\%.\\                  
\gls{CCS} Gas Investment Cost   & Gaussian    & 2626 \$/kW & $\pm$20\%.\\                  
\gls{CCS} Coal Investment Cost  & Gaussian    & 5252 \$/kW & $\pm$20\%.\\
\gls{PWS} Emission Coefficient  & Triangular  & 1.08 g/kWh & 0.2-5.405 g/kWh. \\                  
\gls{SOEC} Emission Coefficient & Triangular  & 1.08 g/kWh & 0.2-5.405 g/kWh. \\
\gls{PWS} Efficiency            & Triangular  & 0.525 & 0.5-0.58. \\                               
\hline
	\end{tabularx}
\label{sa-vars}
\end{table}

### 2021-01-19 publications/2020-03-paper/results.tex
table width fix
Former-commit-id: 48bd34588605351dc3be18710626a4a0bd8db887
Former-commit-id: 2a45e7c4708f82a2238db5736b4c5c97a327f318
spell check, references corrected
Former-commit-id: 7437cf8ebb93536124042c19b07afd5e525608af
Former-commit-id: eb7ea29474615346eeb1e9bba398b6519a449cb7
incorporates the last of kdh comments, closes #98 #99
Former-commit-id: a009126bcf29f293c8ef7aeda35d1402a6cfb4c2
Former-commit-id: bf3d6a2e2d208737784bc145af251c1a2db4774b

\begin{table}[!ht]
	\caption{Summary of decarbonisation simulations' results.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.1\textwidth} p{0.2\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.2\textwidth}p{0.2\textwidth}}
		\hline
\textbf{Scenario} & \textbf{Enabled} & \textbf{Meets} & \textbf{Meets} & \textbf{Emissions} & \textbf{Cost} \\
 & \textbf{Technologies} & \textbf{2030} & \textbf{2050} & \textbf{between} & (USD 2015) \\
 &  & \textbf{emission} & \textbf{emission} & \textbf{2050-2100} &  \\
 &  & \textbf{goals} & \textbf{goals} & &  \\
\hline
1 & Conventional tech., no new nuclear & Yes & No & +25 Mt & 3.51 trillion. \\
2 & Conventional tech., with new nuclear & Yes & Yes & -12 Mt & 2.66 trillion. \\
3 & Emerging tech., no new nuclear & Yes & Yes & No change & 3.19 trillion. \\
4 & Emerging tech., with new nuclear & Yes & Yes & -32 Mt & 2.80 trillion. \\
5 & Nascent tech., no new nuclear & Yes & Yes & No change & 3.18 trillion. \\
\hline 
	\end{tabularx}
\label{tab:results_summary}
\end{table}

In Scenario 1 (Figure \ref{scen1}), the model is able to meet 2030 emission goals but fails to achieve the 2050 target by a margin of 25 Mt. Emissions continue to increase by another 25 Mt by 2100, primarily due to life cycle emissions from lithium-ion storage. As in all other scenarios, coal and oil must be retired by 2030. Natural gas sees rapid growth in the near-term, but complete retirement by 2055. Once deep emission cuts have been achieved, new natural gas is deployed again from 2071 onwards for its load-following capabilities. All existing nuclear power plants must be restarted by 2022 at full operating capacity. With renewable energy as the only option for decarbonisation, significant investments in solar, onshore wind, offshore wind (both fixed-bottom and floating), and lithium-ion storage are necessary. The presence of a large share of renewables results in significant overgeneration of electricity during some years. The amount of electricity diverted to storage technologies over the entire simulation time frame is 46,342 TWh, primarily from solar (36\%), onshore wind (22\%), fixed-bottom offshore wind (22\%),and floating offshore wind (12\%). The total cost of this transition is \textbf{3.51 trillion USD} (in 2015 USD).

\begin{figure}[H] 
\centering
%\vspace*{-3cm}
%\hspace{-3cm}
\includegraphics[scale=0.5]{figures/conv_nonuc}
\caption{Scenario 1 results (conventional technologies without new nuclear). The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
\label{scen1}
\end{figure}

@@

\begin{figure}[H] 
\centering
%\vspace*{-3cm}
\includegraphics[scale=0.5]{figures/conv_nuc}
\caption{Scenario 2 results (conventional technologies with new nuclear). The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
\label{scen2}
\end{figure}

@@

\begin{figure}[H] 
\centering
%\vspace*{-3cm}
\includegraphics[scale=0.5]{figures/newtechs_nonuc}
\caption{Scenario 3 results (emerging technologies without new nuclear). The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
\label{scen3}
\end{figure}

@@

\begin{figure}[H] 
\centering
%\vspace*{-3cm}
\includegraphics[scale=0.5]{figures/newtechs_nuc}
\caption{Scenario 4 results (emerging technologies with new nuclear). The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
\label{scen4}
\end{figure}

@@

\begin{figure}[H] 
\centering
%\vspace*{-3cm}
\includegraphics[scale=0.5]{figures/lowtrltech_nonuc}
\caption{Scenario 5 results (emerging technologies and nascent hydrogen technologies without new nuclear). The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
\label{scen5}
\end{figure}

@@

\begin{figure}[H] 
\centering
\hspace*{-1cm}
\includegraphics[scale=0.7]{figures/syscost_abbrv}
\caption{Sensitivity analysis for overall transition cost vs. solid oxide fuel cell capital costs.}
\label{syscost-smol}
\end{figure}

\begin{figure}[H] 
\centering
%\hspace*{-3cm}
\includegraphics[scale=0.7]{figures/satechselc_abbrv}
\caption{Sensitivity analysis results for electricity supply shares of solid oxide fuel cells (top) and carbon capture and sequestration natural gas plants (bottom) vs solid oxide fuel cell capital costs.}
\label{satechs-smol}
\end{figure}

>>>>

In Scenario 1 (Figure \ref{scen1}), the model is able to meet 2030 emission goals but fails to achieve the 2050 target by a margin of 25 Mt. Emissions continue to increase by another 25 Mt by 2100, primarily due to life cycle emissions from lithium-ion storage. As in all other scenarios, coal and oil must be retired by 2030. Natural gas sees rapid growth in the near-term, but complete retirement by 2055. Once deep emission cuts have been achieved, new natural gas is deployed again from 2071 onwards for its load-following capabilities. All existing nuclear power plants must be restarted by 2022 at full operating capacity. With renewable energy as the only option for decarbonisation, significant investments in solar, onshore wind, offshore wind (both fixed-bottom and floating), and lithium-ion storage are necessary. The presence of a large share of renewables results in significant overgeneration of electricity during some years. The amount of electricity diverted to storage technologies over the entire simulation time frame is 46,342 TWh, primarily from solar (36\%), onshore wind (22\%), fixed-bottom offshore wind (22\%),and floating offshore wind (12\%). The total cost of this transition is \textbf{3.51 trillion USD}.

\begin{figure}[b!] 
\centering
%\vspace*{-3cm}
%\hspace{-3cm}
\includegraphics[scale=0.5]{figures/conv_nonuc}
\caption{Scenario 1 results (conventional technologies without new nuclear). The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
\label{scen1}
\end{figure}

@@

\begin{figure}[b!] 
\centering
%\vspace*{-3cm}
\includegraphics[scale=0.5]{figures/conv_nuc}
\caption{Scenario 2 results (conventional technologies with new nuclear). The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
\label{scen2}
\end{figure}

@@

\begin{figure}[b!] 
\centering
%\vspace*{-3cm}
\includegraphics[scale=0.5]{figures/newtechs_nonuc}
\caption{Scenario 3 results (emerging technologies without new nuclear). The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
\label{scen3}
\end{figure}

@@

\begin{figure}[b!] 
\centering
%\vspace*{-3cm}
\includegraphics[scale=0.5]{figures/newtechs_nuc}
\caption{Scenario 4 results (emerging technologies with new nuclear). The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
\label{scen4}
\end{figure}

@@

\begin{figure}[b!] 
\centering
%\vspace*{-3cm}
\includegraphics[scale=0.5]{figures/lowtrltech_nonuc}
\caption{Scenario 5 results (emerging technologies and nascent hydrogen technologies without new nuclear). The plot at the top shows the electricity generation mix used to meet the demand, the bottom-left figure shows the nameplate capacities of electricity generation and storage technologies that are deployed to meet the demand, and the bottom-right figure shows the sources of emission(direct and life cycle) resulting from this energy mix.}
\label{scen5}
\end{figure}

\begin{table}[!ht]
	\caption{Summary of decarbonisation simulations' results.}
	\vspace{0.1in}
	\begin{tabularx}{0.9\textwidth}{p{0.1\textwidth} p{0.2\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.1\textwidth}p{0.2\textwidth}}
		\hline
\textbf{Scenario} & \textbf{Enabled} & \textbf{Meets} & \textbf{Meets} & \textbf{Emissions} & \textbf{Cost} \\
 & \textbf{Technologies} & \textbf{2030} & \textbf{2050} & \textbf{between} & (USD) \\
 &  & \textbf{emission} & \textbf{emission} & \textbf{2050-} &  \\
 &  & \textbf{goals} & \textbf{goals} & \textbf{2100} &  \\
\hline
1 & Conventional tech., no new nuclear & Yes & No & +25 Mt & 3.51 trillion. \\
2 & Conventional tech., with new nuclear & Yes & Yes & -12 Mt & 2.66 trillion. \\
3 & Emerging tech., no new nuclear & Yes & Yes & No change & 3.19 trillion. \\
4 & Emerging tech., with new nuclear & Yes & Yes & -32 Mt & 2.80 trillion. \\
5 & Nascent tech., no new nuclear & Yes & Yes & No change & 3.18 trillion. \\
\hline 
	\end{tabularx}
\label{tab:results_summary}
\end{table}

@@

\begin{figure}[b!] 
\centering
\hspace*{-1cm}
\includegraphics[scale=0.7]{figures/syscost_abbrv}
\caption{Sensitivity analysis for overall transition cost vs. solid oxide fuel cell capital costs.}
\label{syscost-smol}
\end{figure}

\begin{figure}[b!] 
\centering
%\hspace*{-3cm}
\includegraphics[scale=0.7]{figures/satechselc_abbrv}
\caption{Sensitivity analysis results for electricity supply shares of solid oxide fuel cells (top) and carbon capture and sequestration natural gas plants (bottom) vs solid oxide fuel cell capital costs.}
\label{satechs-smol}
\end{figure}
